Exposing and Exploring Disputed Statements on the Web

### 2009-05-20 papers/uist_thinklink/uist_rebuttal_v2.txt

Reviewers were primarily concerned with two issues: (i) a perceived lack of noverty WRT previous annotation systems and (ii) bootstrapping. We believe that we could easily address both issues with revisions to the paper.

= Novelty =

As reviewer 1 stated: "[Think Link] appears to be the first work to make use of Open Hypermedia for identifying disputed statements on the web".

One could of course use a general-purpose annotation system to do this: if you disagree with something then highlight it, add a comment, or link to opposing evidence.

However this approach raises several issues: Pages could get crowded with noisy "this sucks" comments, users could get frustrated by being told about things they already knew were disputed, and links would not necessarily go to the most useful evidence.

Think Link tries to address these issues by enforcing more structure. A user cannot add an arbitrary comment to a page - instead they must link a snippet to a community-curated claim. A user cannot link a snippet directly to opposing evidence - instead they can add evidence to a claim and hope that the community votes their evidence up.

This structured approach has several user-visible advantages:

* If a user knows something is disputed then they can ask Think Link to not highlight any snippet that makes this claim again.

* Think Link presents the best evidence as voted for by the community, rather than the favorite link chosen by a single user. Similarly, crowdsourcing is used to filter out low quality claims and snippets

* The argumentation graph allows users to see how a claim fits into a larger argument

* Think Link makes it easy for an activist user to rapidly mark many snippets that make the same claim that they disagree with. A common usage model is to Google a sentence, tab-open all pages that look relevant, quickly highlight a relevant snippet in each page, and then bulk-assign all such snippets to the same disputed claim.

= Bootstrapping =

A final version would talk more about bootstrapping.

Our claims are seeded from lists of disputed claims on several websites, including Snopes and several smaller debate web sites. We use Mechanical Turk to produce a seed-set of snippets (4 cents per 10 snippets).

= Misc =

Reviewer 5 was concerned that, since a web page saying global warming did not exist was less popular, it would be less likely to be marked than one that said it did exist. In fact the converse is true. Since there are more activists who believe that global warming exists, more people will use search engines to find and highlight pages that say global warming does not exist, and thus such pages are more likely to be highlighted.

We intend to include a link to several videos in the paper.

Yes, the figures should be bigger.

Think Link does not use IBIS. Our argument graph is simpler than IBIS, but we compare to it since readers may be familiar with it.

### 2009-05-21 papers/uist_thinklink/uist_rebuttal_v2.txt

Reviewers were primarily concerned with two issues: (i) a perceived lack of novelty WRT previous annotation systems and (ii) bootstrapping. We believe that we could easily address both issues with revisions to the paper.

@@

Think Link tries to address these issues by enforcing more structure. A user cannot add an arbitrary comment to a page - instead they must link a snippet to a community-curated claim. A user cannot link a snippet directly to opposing evidence - instead they can add evidence to a claim and hope that the community votes their evidence up.

This structured approach has several user-visible advantages:

* If a user knows something is disputed then they can ask Think Link to not highlight any snippet that makes this claim again.

* Think Link presents the best evidence as voted for by the community, rather than the favourite link chosen by a single user. Similarly, crowd-sourcing is used to filter out low quality claims and snippets

### 2009-05-26 papers/uist_thinklink/uist_rebuttal_v3.txt

There are two key ways we would improve a final draft of this paper: (i) Make it clearer why extra structure makes Think Link work better than a general annotation system for this task and (ii) explain our approach to bootstrapping in more detail.

We will also be happy to address the other helpful suggestions, such as making the figures larger.

= Why additional structure is important =

As reviewer 1 stated: "[Think Link] appears to be the first work to make use of Open Hypermedia for identifying disputed statements on the web".

One could of course use a general-purpose annotation system for this purpose. You could highlight disputed statements, write comments saying things were disputed, and provide links to things you thought were useful evidence.

Think Link is a more specialized tool. Rather than allowing a user to highlight, comment, or link in arbitrary ways, Think Link only permits a user to link a snippet to a claim, link a claim to evidence, link a claim to a related claim, or vote on the quality of links provided by other users.

We believe that this more structure approach provides a significantly improved user experince. In particular:

* Since Think Link knows what claim each snippet is making, Think Link can avoid highlighting disputed claims that the user already knows about.

* When a user clicks on a highlighted claim, they see the best evidence for and against that claim, as determined by the votes of the entire community - rather than the favourite link of use user.

* The argumentation links allow a user to see how a claim fits into a larger argument.

* Voting allows Think Link to filter out lower quality claims/links/snippets and focus on ones the community judged to be more important.

* Think Link makes it easily for an activist user to rapidly mark many snippets that make the same claim that they disagree with. A common usage model is to Google a disputed claim, tab-open all pages that look relevant, quickly highlight a relevant snippet in each page, and then bulk-assign all such snippets to the same disputed claim.

= Bootstrapping =

Bootstrapping is very important for a tool like Think Link. If it does not have a good chance of highlighting pages that the user look it, users will get bored of it.

We have been building a large database of disputed claims by crawling lists of disputed claims from other websites such as Snopes and several political debate web sites. We then use Amazon Mechanical Turk to mark large numbers of snippets for known claims - paying 4 cents per 10 snippets.

Some topics are already very well covered. E.g. we think it would be very difficult for a user to find a page that argued global warming does not exist and that is not highlighted by Think Link.

### 2009-05-28 papers/uist_thinklink/uist_rebuttal_v4.txt

The reviewers were primarily concerned with two issues: 
(i) How is Think Link better than using a general-purpose annotation system to mark disputed claims?
(ii) how can we bootstrap our set of disputed snippets to a big enough size to attract users?

We believe that we can address both issues, as we discuss below.
We will also be happy to address the other helpful suggestions, such as making the figures larger.

= Why additional structure is important =

As reviewer 1 stated: "[Think Link] appears to be the first work to make use of Open Hypermedia for identifying disputed statements on the web".

As several reviewers noted, one could use a general-purpose annotation system for this purpose. You could highlight disputed statements, write comments saying things were disputed, or provide links to things you thought were useful evidence.

Think Link is a more specialized tool. Rather than allowing a user to highlight, comment, or link in arbitrary ways, Think Link only permits a user to link a snippet to a claim, link a claim to evidence, link a claim to a related claim, and vote on the quality of links provided by other users.

We believe that this more structured approach provides an improved user experience. In particular:

* Since Think Link knows what canonical claim each snippet is making, it can avoid highlighting disputed claims that the user already knows about and has requested not be marked again.

* When a user clicks on a highlighted claim, they see the best evidence for and against that claim, as determined by the votes of the entire community - rather than the favourite link of one user.

* The argumentation links allow a user to see how a claim fits into a larger argument.

* Voting allows Think Link to filter out lower quality claims/links/snippets and focus on ones the community judged to be more interesting.

* Think Link makes it easier for an activist user to rapidly mark many snippets that make the same claim. A common usage model is to Google a claim you disagree with, tab-open all pages that look relevant, quickly mark a relevant snippet in each page, and then bulk-assign all marked snippets to the same disputed claim.

= Bootstrapping =

If a user installed Think Link but didn't see anything highlighted then they it is likely they would get bored and stop using it. It is thus important to bootstrap with an initial data set that has reasonable coverage.

This has been problem for previous annotation systems in which the database contained personal annotations specific to particular pages. Fortunately we have found Think Link's restricted domain makes building a data set easier:

Several existing web sites maintain lists of disputed claims. So far we have imported all claims from Snopes and merged in lists taken from several debate websites.

We have found we can pay Mechanical Turk workers 4 cents to mark 10 snippets (using a tool) and 20 cents to create a new disputed claim with snippets and evidence.
